---
title: "Homework 1"
author: Yuanxin Zhang
output: github_document
---

This is my solution to Homework 1. 

```{r}
library(tidyverse)
```


# Question 1
### Part 1: Create a data frame with the specified elements
1. a random sample of size 10 from a standard Normal distribution
2. a logical vector indicating whether elements of the sample are greater than 0
3. a character vector of length 10
4. a factor vector of length 10, with 3 different factor “levels”
```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("small", "small", "medium", "medium", "medium", 
                   "medium", "large", "large", "large", "large"))
  )
```

### Part 2: Take the mean of each variable in data frame
```{r take_mean}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of **numeric** and **logical**, but not **character** or **factor**.

### Part 3: Convert logical, character, and factor variables to numeric variables
```{r convert_part1, results='hide', warning=FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
Logical variable can be converted into meaningful numbers, which explains why we could take the mean of logical variable in the previous chunk.

### Part 4:
1. convert the logical vector to numeric, and multiply the random sample by the result
2. convert the logical vector to a factor, and multiply the random sample by the result
3. convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r convert_part2}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

# Question 2
Load the penguins dataset:
```{r load_data}
data("penguins", package = "palmerpenguins")
```
### Part 1: Write a short description of the penguins dataset
There are `r nlevels(pull(penguins, species))` different species of penguins in the dataset: `r levels(pull(penguins, species))`. Data were collected from `r nlevels(pull(penguins, island))` islands: `r levels(pull(penguins, island))`.
The penguins dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

### Part 2: Make and export a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("p8105_hw1_yz3736_scatterplot.png")
```